Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-10-09 Paper/ms.tex
nu oph references

@@

\begin{thebibliography}{99}
\end{thebibliography}

>>>>

\section{Reanalysis of $\nu$ Oph}
The $\nu$ Oph system is generally accepted to have two confirmed planets
\citep[e.g.][]{2011AIPC.1331..102Q, 2012PASJ...64..135S, fengji}, with periods
of $530.3$ and $3190$ days.

@@

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Hou, Goodman, 
\& Hogg}{2014}]{fengjo} Hou F., Goodman J., Hogg D.~W., 2014, arXiv, arXiv:1401.6128

\bibitem[\protect\citeauthoryear{Quirrenbach, Reffert, 
\& Bergmann}{2011}]{2011AIPC.1331..102Q} Quirrenbach A., Reffert S., Bergmann C., 2011, AIPC, 1331, 102

\bibitem[\protect\citeauthoryear{Sato et al.}{2012}]{2012PASJ...64..135S} 
Sato B., et al., 2012, PASJ, 64, 135 
\end{thebibliography}
